\subsection{Design Science}

Describe what "Design Science" means and how it contributes to the
topic.

\todo{reference papers that describe DS}

\subsection{Empirical Software Engineering}

This section will also introduce terms like "SMS" "SLR" "SGLR", and the general
definition of "Empirical Software Engineering".

\todo{reference papers that describe ESE}

\subsection{Microservices and DevOps}

Introduce terms
like "MSA", "microservice" and "DevOps" so everybody is on the
same page about those terms. Those terms should be introduced by reference
of other papers/articles or even websites.

\section{Summary of Waseem et al.}

This section does summarize the goal, idea and result of the paper.
This part will be a neutral summary.
Give an abstract about the paper of \cite{waseem:SMS}.

\subsection{Motivation}

Describe and analyze the motivation of the researcher group that made the SMS.

\subsection{Methodology}

Analyze and summarize their methods. Describe the process they used and the
additional changes they made to conduct their SMS.

\subsection{Research Questions}

Give a brief summary about their questions that they want to answer in the study.

\subsection{Results}

Summary of the results of the paper.

\subsection{Discussion}

Summary of the given "discussion" in the paper.

\subsection{Threats to validity}

Summary of their threads to validity.

\subsection{Conclusion}

Summary of the given conclusion.

\section{Review of Waseem et al.}

Points to address:
\begin{itemize}
    \item Why 2009 until 2018 (and not 2020 oder 2019)
    \item Day1 / Day2 Optimization
    \item Topic Performance: What about service depth (i.e. "deep services")
\end{itemize}

\subsection{Empirical Research Methods}

Approvement / Disapprovement in the used methods and how they were applied to
the study. Question the decision to limit the search to the year 2018.

\subsection{Research Questions}

Analyze the research question and may give feedback or alternatives to them.

\subsection{Results and Discussion}

Give feedback to the compiled results and the discussion that followed
that results.

\section{MSA in DevOps}

Give an opinionated statement about what MSA in DevOps is and how the study
does support this topic.
Add references to gitops as a modern idea on how solve some problems (because
they weren't in the search params?)

\todo{find papers about day1/2 optimization}

\todo{find papers about gitops}

\section{Conclusion}

Give the conclusion to the review of \cite{waseem:SMS}.
